Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS

### 2023-10-31 paper/ms.tex
update ms (reviewer report)

% upon AAS submission
%\documentclass[12pt,twocolumn,tighten,linenumbers]{aastex63}
%\documentclass[12pt,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
% drafting / arxiv
\documentclass[11pt,twocolumn,tighten]{aastex63}
\turnoffedit

@@

% 250 word max!
\begin{abstract}
  %
  Complex periodic variables (CPVs) are stars that exhibit highly
  structured and periodic optical light curves.  Previous studies have
  indicated that these stars are typically disk-free pre-main-sequence
  M dwarfs with rotation periods ranging from 0.2 to 2 days.  To
  advance our understanding of these enigmatic objects, we conducted a
  blind search using TESS 2-minute data of \nstarssearched\ K and M
  dwarfs with $T$$<$16 and $d$$<$150\,pc.  We found \ngoods\
  high-quality CPVs, and subsequently determined that most are members
  of stellar associations.  Among the new discoveries are the
  brightest ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and
  oldest ($\approx$200\,Myr) CPVs known.  One exceptional object, LP
  12-502, exhibited up to eight flux dips per cycle. Some of these
  dips coexisted with slightly different periods, and the
  shortest-duration dips precisely matched the expected timescale for
  transiting small bodies at the corotation radius.  Broadly, our
  search confirms that CPVs are mostly young ($\lesssim$150\,Myr) and
  low-mass ($\lesssim$0.4\,$M_\odot$).  The flux dips characteristic
  of the class have lifetimes of $\approx$100 cycles, although stellar
  flares seem to induce sudden dip collapse once every few months.
  The most plausible explanation for these phenomena remains
  corotating concentrations of gas or dust.  The gas or dust is
  probably entrained by the star's magnetic field, and the sharp
  features could result from a multipolar field topology, a hypothesis
  supported by correspondences between the light curves of CPVs and of
  rapidly rotating B stars known to have multipolar magnetic fields.
  %
\end{abstract}

@@

We homogeneously assessed whether the objects identified using the
dip-counting (Section~\ref{subsec:counting}) and Fourier
(Section~\ref{subsec:fourier}) approaches were consistent with
expectations for CPVs by assembling the data shown in
Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CPV if it met
all of the following criteria for at least one TESS sector:
\vspace{-2pt}
\begin{itemize}[leftmargin=*]
  \setlength\itemsep{-2pt}
  \item $P<2$\,days.
  %
  \item At least three dips per cycle, or else otherwise oddly-shaped
    dips relative to expectations for quasi-sinusoidal
    starspot-induced modulation.
  %
  \item Persistent dips over multiple consecutive rotation cycles.
\end{itemize}
\vspace{-2pt}
We also noted ''possible'' CPVs for which the classification was more
ambiguous, and ``false positives'' that are definitely not CPVs.  The
most common false positives for both the Fourier and dip-counting
techniques were eclipsing binaries, ordinary spotted rapid rotators,
and light curves that were complex due to multiple stars contributing
to the photometric aperture.  Our specialized dip-counting pipeline
flagged \nuniqdipflagged\ unique stars for visual inspection; about
20\% were subsequently labeled either good or possible CPVs.  From the
more general Fourier pipeline, $\approx$0.5\% of stars that passed the
12-$\sigma$ peak threshold were eventually classified as CPVs.

@@

For a few cases where BANYAN\,$\Sigma$ yielded ambiguous results, we
consulted the meta-catalog of young, age-dated, and age-dateable stars
provided by \citet{2022AJ....163..121B}, and also searched the local
volume around each star for co-moving
companions.\footnote{\url{https://github.com/adamkraus/Comove}, git
commit \texttt{278b372}} Finally, to provide a base for comparison, we
also ran the BANYAN\,$\Sigma$ membership analysis on our entire
\nstarssearched\ target star sample.

@@

With the effective temperatures and stellar radii from the SED fit, we
estimated the stellar masses by interpolating against the PARSEC
isochrones \citep[v1.2S][]{2014MNRAS.444.2525C}.  The need for models
that incorporate some form of correction for young, active M dwarfs is
well-documented
\citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2020ApJ...891...29S}.
Plausible explanations for the disagreement between observed and
theoretical M dwarf colors and sizes include starspot coverage
\citep[e.g.][]{2017ApJ...836..200G} and potentially incomplete line
lists \citep[e.g.][]{2013A&A...556A..15R}.  In the PARSEC models,
\citet{2014MNRAS.444.2525C} performed an empirical correction to the
temperature--opacity relation drawn from the BT-Settl model
atmospheres, in order to match observed masses and radii of young
eclipsing binaries.  This is sufficient for our goal of estimating
stellar masses.  Given our estimates of $\{ \tilde{T}_{\rm eff},
\tilde{M}_\star, \tilde{t} \}$, and approximating their uncertainties
as Gaussian $\sigma_{\tilde{T}_{\rm eff}}$, $\sigma_{\tilde{M}_\star}$
and $\sigma_{\tilde{t}}$, we define a distance metric $\Delta$ to each
model PARSEC grid-point $\{ T_{\rm eff}, M_\star, t \}$ via
\begin{equation}
  \Delta^2 = 
  \left( \frac{\tilde{T}_{\rm eff} - T_{\rm eff}}{\sigma_{\tilde{T}_{\rm eff}}} \right)^2
  +
  \left( \frac{\tilde{M}_{\star} - M_{\star}}{\sigma_{\tilde{M}_{\star}}} \right)^2
  +
  \left( \frac{\tilde{t} - t}{\sigma_{\tilde{t}}} \right)^2,
\end{equation}
where the division by the uncertainties helps to assign equal
importance to each dimension.  The mass reported in
Table~\ref{tab:thetable} is the model mass that minimizes the
distance.  The reported uncertainties in the masses are based on
propagating the statistical uncertainties in the radii, temperatures,
and ages.

@@

{\it Radial velocity scatter}---We examined diagrams of the Gaia DR3
``radial velocity error'' as a function of stellar color for all
\ncqvsnodebunked\ CPVs and candidate CPVs.  Since this quantity
represents the standard deviation of the non-published Gaia RV time
series, outliers can suggest single-lined spectroscopic binarity.
These plots showed two clusters of stars, at $\lesssim$10\,\kms and
20-25\,\kms.  We therefore adopted a threshold of $20$\,km\,s$^{-1}$
to flag possible single-lined spectroscopic binaries, which selected
\nrvscatterflag\ stars: TIC~405910546, TIC~224283342, and
TIC~280945693.

{\it RUWE}---We examined plots of Gaia DR3 RUWE as a function of
color.\footnote{For an explanation of the renormalized unit weight
error (RUWE), see the GAIA DPAC technical note
\url{http://www.rssd.esa.int/doc_fetch.php?  id=3757412}.}  Elevated
RUWEs imply excess astrometric noise relative to a single-source
model.  This can be caused by marginally resolved binaries,  intrinsic
photometric variability, or intrinsic astrometric motion.  Based on
this exercise, we adopted a threshold of RUWE$_{\rm DR3}>2$ to flag
sources with excess astrometric noise.  This threshold was met by
\ngoodhighruwe/\ngoods\ high-quality CPVs and by
\nmaybehighruwe/\nmaybes\ of the ambiguous CPVs.  The choice of the
threshold RUWE is somewhat subjective, since the RUWE distribution has
an extended tail \citep[e.g.][]{2022MNRAS.513.5270P}.  If we had
instead required RUWE$_{\rm DR3}>1.4$, \ngoodweakruwe/\ngoods\
high-quality CPVs and \nmaybeweakruwe/\nmaybes\ of the ambiguous
sample would have been flagged.

@@

Most CPVs in our catalog did not show infrared excesses in the
$W1$-$W4$ bands, which is typical for this class of object
\citep{2017AJ....153..152S}.  Visually inspecting the SEDs of our
\nallcands\ star sample and the WISE images available through IRSA, we
labeled two objects as having reliable infrared excesses (both $W3$
and $W4$ fluxes are more than 3$\sigma$ above the photospheric
prediction): TIC~193136669 (TWA~34) and TIC~57830249 (TWA~33).
However, neither is considered a ``good'' CPV for the reasons that
follow.

@@

\subsubsection{Multiple CPVs in the same system: TIC~425937691 and TIC~142173958}

@@

For CPVs, binarity seems to provide either nuisances or curiosities.
The nuisances include astrophysical false positives with two beating
rapidly rotating stars, as well as uncertainty about which star
produces the CPV signal in binary systems.  Our two candidate K dwarf
CPVs suffer from this latter concern (see
Section~\ref{subsec:resultsbinarity}).

Curiosities include the four binary systems that are now known to each
host two separate CPVs.  CPVs are sufficiently rare that such systems
may have physical import.  Recent work has shown that the orbits of
binaries closer than $\lesssim$700 AU tend to be aligned with their
planetary systems \citep[e.g.][]{2022AJ....163..207C}.  If we assume
that observing CPV variability requires high line-of-sight
inclinations, and that the inclinations in binaries are correlated,
then we would expect the detection of one CPV in a binary system to
raise the probability that the other star is a CPV.  The limitations
of the current catalog prevent further exploration of this issue, but
it might be interesting for future study.

A separate possible relation between binarity and CPVs is that the
presence of a binary companion could cause early disk dispersal,
freeing the star to contract.  The CPV phenomenon seems to require
rapid rotation; thus if binary systems tend to produce more rapidly
rotating stars, we would expect a sample of CPVs to have a larger
binary fraction than the field.  However, we see minimal evidence for
such an effect (Section~\ref{subsec:resultsbinarity}).  The
multiplicity rate of M dwarfs near the Sun is 26.8$\pm$1.4\%
\citep{2019AJ....157..216W}.  The $\approx$32\% multiplicity fraction
in our CPV sample (from RUWE$_{\rm DR3}$; see
Section~\ref{subsec:resultsbinarity}) seems approximately consistent
with this field fraction.

@@

The observed lifetime of the CPV phenomenon could provide another way
to discern between the gas and dust clump scenarios.  Based on the
available statistics from \deleted{e.g. }\citet{2022AJ....164...80R} and
references therein, it seems plausible that CPV occurrence decreases
with stellar age from $\approx$3\% at 10\,Myr (Sco-Cen), to
$\approx$1\% at 100\,Myr (Pleiades), down to 0\% by the
$\approx$700\,Myr age of Praesepe.  This is odd in the context of the
prominence scenario, because pre-main-sequence M dwarfs spin up over
the first 100\,Myr; prominences might therefore be expected to be {\it
more} common at 100\,Myr than at 10\,Myr, under the assumption that
the production of prominences depends only on the stellar rotation
rate.  The dust clump scenario would hold a natural explanation: the
lower occurrence of CPVs around older stars would simply reflect a
finite supply of dust.  One possible complication however is that the
magnetic field topology of rapidly rotating M dwarfs may depend on
factors other than the rotation rate (e.g.\ the age), which might
alter the production of prominences.

@@

\acknowledgments
LGB is grateful for support from the Heising-Simons 51~Pegasi~b
Fellowship, and for helpful conversations with J.~Spake, A.~Mann,
G.~Laughlin, and B.~Draine.  
We are also grateful for the assistance of S.~Yee, L.~Weiss,
H.~Isaacson, and A.~Howard in acquiring and reducing the HIRES
spectra.
This paper relied primarily on data collected by the TESS mission; the
specific 2-minute cadence observations can be accessed via
DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.
Funding for the TESS mission is provided by NASA’s Science Mission
Directorate.  
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, and J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success. 
LP 12-502 in particular was observed at 2-minute cadence thanks to the
TESS Guest Investigator programs G022252 (PI: J.~Schlieder; Sectors
18, 19, 25, 26) and G04168 (PI: R.~Jayaraman; Sector 53). 
ADU acknowledges support by NASA under award number 80GSFC21M0002, as
well as ROSES award 22-ADAP22-0070.

@@

\facilities{
 	{\it Astrometry}:
		Gaia \citep{2018A&A...616A...1G,2023A&A...674A...1G}.
 	{\it Imaging}:
    Second Generation Digitized Sky Survey. %,
    %SOAR~(HRCam; \citealt{tokovinin_ten_2018}).
		%Keck:II~(NIRC2).
		%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
		%Gemini:North~(`Alopeke; \citealt{scott_nessi_2018,scott_twin_2021}.
 	{\it Spectroscopy}:
		%CTIO1.5$\,$m~(CHIRON; \citealt{tokovinin_chironfiber_2013}),
		%PFS ({\bf CITE}),
		%Tillinghast:1.5m~(TRES).
		%MPG2.2$\,$m~(FEROS; \citealt{kaufer_commissioning_1999}),
		%AAT~(Veloce; \citealt{gilbert_veloce_2018}).
		%AAT~(HERMES; \citealt{lewis_2002_hermers_2df,sheinis_2015_hermes}),
		Keck:I~(HIRES; \citealt{1994SPIE.2198..362V}).
		%VLT:Kueyen~(FLAMES; \citealt{pasquini_2002}).
 	  %Euler1.2m~(CORALIE),
 	  %ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
 	{\it Photometry}:
		%ASTEP:0.40$\,$m (ASTEP400),
		%CTIO:1.0m (Y4KCam),
		%Danish 1.54m Telescope,
		%El Sauce:0.356$\,$m,
		%Elizabeth 1.0m at SAAO,
		%Euler1.2m (EulerCam),
		%Kepler,
		%Magellan:Baade (MagIC),
		%Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
		%MuSCAT3 \citep{Narita_2020},
		%NTT,
		%SOAR (SOI),
 	  TESS \citep{2015JATIS...1a4003R},
		%TRAPPIST \citep{jehin_trappist_2011},
		%VLT:Antu (FORS2).
		%ZTF.
  {\it Broadband photometry}:
    2MASS \citep{2006AJ....131.1163S},
    APASS \citep{2016yCat.2336....0H},
		Gaia \citep{2018A&A...616A...1G,2023A&A...674A...1G},
    SDSS \citep{2000AJ....120.1579Y},
    WISE \citep{2010AJ....140.1868W}.
}

>>>>

% upon AAS submission
%\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex63}
\documentclass[11pt,twocolumn,tighten,linenumbers,trackchanges]{aastex63}
% drafting / arxiv
%\documentclass[11pt,twocolumn,tighten,linenumbers]{aastex63}
%\turnoffedit

@@

% 250 word max!
\begin{abstract}
  %
  Complex periodic variables (CPVs) are stars that exhibit highly
  structured and periodic optical light curves.  Previous studies have
  indicated that these stars are typically disk-free pre-main-sequence
  M dwarfs with rotation periods ranging from 0.2 to 2 days.  To
  advance our understanding of these enigmatic objects, we conducted a
  blind search using TESS 2-minute data of \nstarssearched\ K and M
  dwarfs with $T$$<$16\added{\,mag} and $d$$<$150\,pc.  We found \ngoods\
  high-quality CPVs, and subsequently determined that most are members
  of stellar associations.  Among the new discoveries are the
  brightest ($T$$\approx$9.5\added{\,mag}), closest ($d$$\approx$20\,pc), and
  oldest ($\approx$200\,Myr) CPVs known.  One exceptional object, LP
  12-502, exhibited up to eight flux dips per cycle. Some of these
  dips coexisted with slightly different periods, and the
  shortest-duration dips precisely matched the expected timescale for
  transiting small bodies at the corotation radius.  Broadly, our
  search confirms that CPVs are mostly young ($\lesssim$150\,Myr) and
  low-mass ($\lesssim$0.4\,$M_\odot$).  The flux dips characteristic
  of the class have lifetimes of $\approx$100 cycles, although stellar
  flares seem to induce sudden dip collapse once every few months.
  The most plausible explanation for these phenomena remains
  corotating concentrations of gas or dust.  The gas or dust is
  probably entrained by the star's magnetic field, and the sharp
  features could result from a multipolar field topology, a hypothesis
  supported by correspondences between the light curves of CPVs and of
  rapidly rotating B stars known to have multipolar magnetic fields.
  %
\end{abstract}

@@

We homogeneously assessed whether the objects identified using the
dip-counting (Section~\ref{subsec:counting}) and Fourier
(Section~\ref{subsec:fourier}) approaches were consistent with
expectations for CPVs by assembling the data shown in
Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CPV if it met
all of the following criteria for at least one TESS sector:
\vspace{-2pt}
\begin{itemize}[leftmargin=*]
  \setlength\itemsep{-2pt}
  \item $P<2$\,days.
  %
  \item At least three dips per cycle, or else otherwise oddly-shaped
    dips relative to expectations for quasi-sinusoidal
    starspot-induced modulation.
  %
  \item Persistent dips over multiple consecutive rotation cycles.
\end{itemize}
\vspace{-2pt}
We also noted \replaced{''possible'' CPVs for which the classification
was more ambiguous, and}{a few stars with potentially oddly-shaped dips
as ``ambiguous'' CPVs, and a few interesting} ``false
positives'' that are definitely not CPVs.  The most common false
positives for both the Fourier and dip-counting techniques were
eclipsing binaries, ordinary spotted rapid rotators, and light curves
that were complex due to multiple stars contributing to the
photometric aperture.  Our specialized dip-counting pipeline flagged
\nuniqdipflagged\ unique stars for visual inspection; about 20\% were
subsequently labeled either good or \replaced{possible}{ambiguous} CPVs.  From the more
general Fourier pipeline, $\approx$0.5\% of stars that passed the
12-$\sigma$ peak threshold were eventually classified as CPVs.

@@

For a few cases where BANYAN\,$\Sigma$ yielded ambiguous results, we
consulted the meta-catalog of young, age-dated, and age-dateable stars
\replaced{provided}{assembled} by \citet{2022AJ....163..121B}, and also searched the local
volume around each star for co-moving
companions.\footnote{\url{https://github.com/adamkraus/Comove}, git
commit \texttt{278b372}\added{; see also \citet{2021AJ....161..171T}.}}\added{ A few important sources in the former meta-catalog included the
Theia groups from \citet{KounkelCovey2019} and \citet{2020AJ....160..279K}, and the SPYGLASS stars from Table~1 of \citet{2021ApJ...917...23K}.} Finally, to provide a base for comparison, we
also ran the BANYAN\,$\Sigma$ membership analysis on our entire
\nstarssearched\ target star sample.

@@

With the effective temperatures and stellar radii from the SED fit, we
estimated the stellar masses by interpolating against the PARSEC
isochrones \citep[v1.2S;][]{2014MNRAS.444.2525C}.  The need for models
that incorporate some form of correction for \deleted{young, active }M dwarfs is
well-documented \citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2018AJ....155..225K,2019MNRAS.489.2615M,2020ApJ...891...29S}.
Plausible explanations for the disagreement between observed and
theoretical M dwarf colors and sizes include starspot coverage
\citep[e.g.][]{2017ApJ...836..200G} and \deleted{potentially }incomplete line
lists \citep[e.g.][]{2013A&A...556A..15R}.  In the PARSEC models,
\citet{2014MNRAS.444.2525C} performed an empirical correction to the
temperature--opacity relation drawn from the BT-Settl model
atmospheres, in order to match observed masses and radii of young
eclipsing binaries.  This is sufficient for our goal of estimating
stellar masses.  Given our estimates of $\{ \tilde{T}_{\rm eff},
\tilde{R}_\star, \tilde{t} \}$, and approximating their uncertainties
as Gaussian $\sigma_{\tilde{T}_{\rm eff}}$, $\sigma_{\tilde{R}_\star}$
and $\sigma_{\tilde{t}}$, we define a distance metric $\Delta$ to each
model PARSEC grid-point $\{ T_{\rm eff}, R_\star, t \}$ via
\begin{equation}
  \Delta^2 = 
  \left( \frac{\tilde{T}_{\rm eff} - T_{\rm eff}}{\sigma_{\tilde{T}_{\rm eff}}} \right)^2
  +
  \left( \frac{\tilde{R}_{\star} - R_{\star}}{\sigma_{\tilde{R}_{\star}}} \right)^2
  +
  \left( \frac{\tilde{t} - t}{\sigma_{\tilde{t}}} \right)^2,
\end{equation}
where the division by the uncertainties helps to assign equal
importance to each dimension.  The mass reported in
Table~\ref{tab:thetable} is the model mass that minimizes the
distance.  The reported uncertainties in the masses are based on
propagating the statistical uncertainties in the radii, temperatures,
and ages.

@@

{\it Radial velocity scatter}---We examined diagrams of the Gaia DR3
``radial velocity error'' as a function of stellar color for all
\ncqvsnodebunked\ CPVs and candidate CPVs.  Since this quantity
represents the standard deviation of the non-published Gaia RV time
series, outliers can suggest single-lined spectroscopic binarity\added{ \citep[e.g.][]{2022arXiv220611275C}}.  These plots showed two
clusters of stars, at $\lesssim$10\,\kms and
20-25\,\kms.  We therefore adopted a threshold of $20$\,km\,s$^{-1}$
to flag possible single-lined spectroscopic binaries, which selected
\nrvscatterflag\ stars: TIC~405910546, TIC~224283342, and
TIC~280945693.

{\it RUWE}---We examined plots of Gaia DR3 RUWE as a function of
color.\footnote{For an explanation of the renormalized unit weight
error (RUWE), see the GAIA DPAC technical note
\url{http://www.rssd.esa.int/doc_fetch.php?  id=3757412}.}  Elevated
RUWEs imply excess astrometric noise relative to a single-source
model.  This can be caused by marginally resolved binaries,  intrinsic
photometric variability, or intrinsic astrometric motion\added{
\citep[e.g.][]{2021AJ....162..128W}}.  Based on this exercise, we
adopted a threshold of RUWE$_{\rm DR3}>2$ to flag
sources with excess astrometric noise.  This threshold was met by
\ngoodhighruwe/\ngoods\ high-quality CPVs and by
\nmaybehighruwe/\nmaybes\ of the ambiguous CPVs.  The choice of the
threshold RUWE is somewhat subjective, since the RUWE distribution has
an extended tail \citep[e.g.][]{2022MNRAS.513.5270P}.  If we had
instead required RUWE$_{\rm DR3}>1.4$, \ngoodweakruwe/\ngoods\
high-quality CPVs and \nmaybeweakruwe/\nmaybes\ of the ambiguous
sample would have been flagged.

@@

Most CPVs in our catalog did not show infrared excesses in the
$W1$-$W4$ bands, which is typical for this class of object
\citep{2017AJ....153..152S}.  \replaced{Visually inspecting}{Inspecting} the SEDs of our
\nallcands\ star sample and the WISE images available through IRSA, we
labeled two objects as having reliable infrared excesses (both $W3$
and $W4$ fluxes are more than 3$\sigma$ above the photospheric
prediction): TIC~193136669 (TWA~34) and TIC~57830249 (TWA~33).
However, neither is considered a ``good'' CPV for the reasons that
follow.

@@

\subsubsection{Multiple CPVs in the same system: TIC~425937691 and TIC~142173958}
\label{subsec:multis}

@@

For CPVs, binarity seems to provide either nuisances or curiosities.
The nuisances include astrophysical false positives with two beating
rapidly rotating stars, as well as uncertainty about which star
produces the CPV signal in binary systems.  Our two candidate K dwarf
CPVs suffer from this latter concern (see
Section~\ref{subsec:massive}).

Curiosities include the four binary systems that are now known to each
host two separate CPVs \added{(see Section~\ref{subsec:multis})}.  CPVs are sufficiently rare that such systems
may have physical import.  Recent work has shown that the orbits of
binaries closer than $\lesssim$700 AU tend to be aligned with their
planetary systems \citep[e.g.][]{2022AJ....163..207C}.  If we assume
that observing CPV variability requires high line-of-sight
inclinations, and that the inclinations in binaries are correlated,
then we would expect the detection of one CPV in a binary system to
raise the probability that the other star is a CPV.  The limitations
of the current catalog prevent further exploration of this issue, but
it might be interesting for future study.

\deleted{A separate possible relation between binarity and CPVs is that the
presence of a binary companion could cause early disk dispersal,
freeing the star to contract.  The CPV phenomenon seems to require
rapid rotation; thus if binary systems tend to produce more rapidly
rotating stars, we would expect a sample of CPVs to have a larger
binary fraction than the field.  However, we see minimal evidence for
such an effect (Section~\ref{subsec:resultsbinarity}).  The
multiplicity rate of M dwarfs near the Sun is 26.8$\pm$1.4\%
\citep{2019AJ....157..216W}.  The $\approx$32\% multiplicity fraction
in our CPV sample (from RUWE$_{\rm DR3}$; see
Section~\ref{subsec:resultsbinarity}) seems approximately consistent
with this field fraction.}

@@

The observed lifetime of the CPV phenomenon could provide another way
to discern between the gas and dust clump scenarios.  Based on the
available statistics from \deleted{e.g. }\citet{2022AJ....164...80R} and
references therein, it seems plausible that CPV occurrence decreases
with stellar age from $\approx$3\% at 10\,Myr (Sco-Cen), to
$\approx$1\% at 100\,Myr (Pleiades), down to 0\% by the
$\approx$700\,Myr age of Praesepe.  This is odd in the context of the
prominence scenario, because pre-main-sequence M dwarfs spin up over
the first 100\,Myr; prominences might therefore be expected to be {\it
more} common at 100\,Myr than at 10\,Myr, under the assumption that
the production of prominences depends only on the stellar rotation
rate.  The dust clump scenario would hold a natural explanation: the
lower occurrence of CPVs around older stars would simply reflect a
finite supply of dust.  One \replaced{possible}{potential} complication however is that the
magnetic field topology of rapidly rotating M dwarfs may depend on
factors other than the rotation rate (e.g.\ the age), which might
alter the production of prominences.

\added{\subsection{Why are the dip and spot periods nearly equal?}}

\added{The CPV dips are usually superposed on nearly sinusoidal modulation.
The sinusoidal modulation
is probably induced by brightness inhomogeneities on the stellar surface.  If
the dips are explained by material orbiting the star, then the proximity
of the spot and dip periods is surprising.
For instance, the dust clumps modeled by \citet{2023MNRAS.518.4734S} tend to
accumulate near -- but not exactly at -- corotation.}

\added{To explore the proximity of the dip and spot periods, we
generated synthetic light curves that superposed a sinusoid and a single
eclipse.  We imposed periods, amplitudes, sampling, and noise properties
similar to typical CPVs in Figure~\ref{fig:cpvs}.  We then tuned
the period of the eclipse signal to differ slightly from the
sinusoidal period, and processed the resulting synthetic signals
through the same period-finding routine to which we subjected the real data.
Provided the dip and sinusoid periods agreed to within $\approx$0.1\%, we found that
phase-folding on the dominant period (that of the larger-amplitude starspots)
yielded dip signals analogous to those in Figure~\ref{fig:cpvs}.  However
increasing the period difference beyond $\gtrsim$0.3\%, the dip signal quickly becomes
``smeared'' out and unidentifiable when phase-folding.  This
exercise highlights that our search was sensitive only to stars with dip
and spot periods that agreed to within a few parts per thousand.  
Some CPVs may exceed this threshold; we encourage
future work aimed at determining whether such stars exist.}

@@

\acknowledgments
LGB is grateful for support from the Heising-Simons 51~Pegasi~b
Fellowship, and for helpful conversations with J.~Spake, A.~Mann,
G.~Laughlin, and B.~Draine.  
We are also grateful for the assistance of S.~Yee, L.~Weiss,
H.~Isaacson, and A.~Howard in acquiring and reducing the HIRES
spectra\added{, and for the reviewer's suggestion to consider
the proximity of the dip and spot periods}.
This paper relied primarily on data collected by the TESS mission; the
specific 2-minute cadence observations can be accessed via
DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.
Funding for the TESS mission is provided by NASA’s Science Mission
Directorate.  
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, and J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success. 
LP 12-502 in particular was observed at 2-minute cadence thanks to the
TESS Guest Investigator programs G022252 (PI: J.~Schlieder; Sectors
18, 19, 25, 26) and G04168 (PI: R.~Jayaraman; Sector 53). 
ADU acknowledges support by NASA under award number 80GSFC21M0002, as
well as ROSES award 22-ADAP22-0070.

@@

\facilities{
 	{\it Astrometry}:
		Gaia \citep{2018A&A...616A...1G,2023A&A...674A...1G}.
 	{\it Imaging}:
    Second Generation Digitized Sky Survey. %,
    %SOAR~(HRCam; \citealt{tokovinin_ten_2018}).
		%Keck:II~(NIRC2).
		%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
		%Gemini:North~(`Alopeke; \citealt{scott_nessi_2018,scott_twin_2021}.
 	{\it Spectroscopy}:
		%CTIO1.5$\,$m~(CHIRON; \citealt{tokovinin_chironfiber_2013}),
		%PFS ({\bf CITE}),
		%Tillinghast:1.5m~(TRES).
		%MPG2.2$\,$m~(FEROS; \citealt{kaufer_commissioning_1999}),
		%AAT~(Veloce; \citealt{gilbert_veloce_2018}).
		%AAT~(HERMES; \citealt{lewis_2002_hermers_2df,sheinis_2015_hermes}),
		Keck:I~(HIRES; \citealt{1994SPIE.2198..362V}).
		%VLT:Kueyen~(FLAMES; \citealt{pasquini_2002}).
 	  %Euler1.2m~(CORALIE),
 	  %ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
 	{\it Photometry}:
		%ASTEP:0.40$\,$m (ASTEP400),
		%CTIO:1.0m (Y4KCam),
		%Danish 1.54m Telescope,
		%El Sauce:0.356$\,$m,
		%Elizabeth 1.0m at SAAO,
		%Euler1.2m (EulerCam),
		%Kepler,
		%Magellan:Baade (MagIC),
		%Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
		%MuSCAT3 \citep{Narita_2020},
		%NTT,
		%SOAR (SOI),
 	  TESS \citep{2015JATIS...1a4003R},
		%TRAPPIST \citep{jehin_trappist_2011},
		%VLT:Antu (FORS2).
		%ZTF.
  {\it Broadband photometry}:
    2MASS \citep{2006AJ....131.1163S},
    APASS \citep{2016yCat.2336....0H},
		Gaia \citep{2018A&A...616A...1G,2023A&A...674A...1G},
    SDSS \citep{2000AJ....120.1579Y},
    WISE \citep{2010AJ....140.1868W,2014yCat.2328....0C}.
}
